Investigating the Safety of Different Toronto Neighbourhoods in 2011 Based on The Number of Crimes Reported

### 2024-09-27 paper/paper.qmd
Updated discussion. Updated title of Rproj File

Based on what was seen in the data, the Toronto neighbourhoods with the highest total number of major crimes can be easily determined. According to what was shown in the bar graph (@fig-total_crimes_top_50), neighbourhoods located near the South part of the Greater Toronto Area (GTA), especially Downtown regions of the city, were highly represented in the top 50 for total crimes.

One interpretation is that this indicates that the safety of the downtown region is considerably lower than other regions of the city. The city departments that play a role in citizen regulation and safety control may be less competent than those departments in regions with lower numbers of total major crime incidents. On a similar note, the social status and financial ability of people in different neighbourhoods vary. Those neighbourhoods with higher numbers of crime could be the ones where preferred victims of criminals live.

@@

The potential reasons behind assault numbers being correlated to the total number of major crimes can vary largely. One way of interpreting this relationship is that, people who commit assault crimes tend to do so in neighbourhoods that have more crime overall. This tendency is stronger than people committing other types of crimes. Many other potential explanations may be valid. Further research would be required for a specific conclusion on the reason behind this correlation.

@@

>>>>

Based on what was seen in the data, the Toronto neighbourhoods with the highest total number of major crimes can be easily determined. According to what was shown in the bar graph (@fig-total_crimes_top_50), neighbourhoods that were highest in total number of crimes tended to be located towards the South part of the Greater Toronto Area (GTA), especially Downtown regions of the city. The higher crime numbers can be interpreted as an overall well-being of the community and the safety of the neighbourhood, as indicated in the original data set (@TorontoSafety).

One interpretation is that this indicates that the safety of the downtown region is considerably lower than other regions of the city. The city departments that play a role in citizen regulation and safety control may be less competent than those departments in regions with lower numbers of total major crime incidents. On a similar note, the social status and financial ability of people in different neighbourhoods vary. Those neighbourhoods with higher numbers of crime could be the ones where preferred victims of criminals live or where criminals themselves tend to reside.

@@

The potential reasons behind assault numbers being correlated to the total number of major crimes can vary largely. This can interpret One way of interpreting this relationship is that, people who commit assault crimes tend to do so in neighbourhoods that have more crime overall. This tendency is stronger than people committing other types of crimes. Many other potential explanations may be valid. Further research would be required for a specific conclusion on the reason behind this correlation.

@@

A final weakness is the timeliness of this data. The data set is from 2011, which is out of date to be used for analysis of more recent trends. The neighbourhood crime numbers could have shifted largely since 2011. There may have also been expansions of the city, where many neighbourhoods present today may not have been present in 2011. This means that the data that is looked at in this paper may not be the best source to use to make residence suggestions to people living in the city today. To improve this, a more recent set of data must be used. Similar ways of analyzing the data can be done to achieve the effects of suggesting residency for the current population.
